Supporting Information:\\Accurate binding of sodium and calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-11-16 Manuscript/SI.tex
Minor changes SI

The results from simulations are shown in Fig.~\ref{fig:cacl-bind}
together with the line fitted to experimental data by Altenbach and Seelig~\cite{altenbach84}.
Both results are in agreement with the prediction of the ternary complex model.
The small discrepancy between the results from experiments and simulations probably
arise from difference in the evaluation of the concentrations and
inaccuracy of Poisson-Boltzmann theory for divalent cations like \ce{Ca^{2+}}~\cite{Andelman1995}. 
In conclusion, the results suggest that the almost equal probabilities for
\ce{Ca^{2+}} to form complexes with 1-3 lipids observed in the main text is,
indeed, in line with the experimental observations supporting the ternary complex model.
\newpage
\begin{figure}[!h]
  \centering
  \includegraphics[height=9.0cm,angle=-90]{../Fig/bound-CAs_conc-eccl17.eps}
  \caption{\label{fig:cacl-bind}
    Fits of experimental~\cite{altenbach84} and ECC-POPC simulation data to
    the prediction of the ternary complex model.
    {\color{red} Joe, please change the axes labels to correspond the notation in the text, i.e. $C_b$ and $C_I$,
    and write in the title of simulation fit (red dashed line) that it is the fit to simulation.}
    %Ternary complex binding model of \ce{Ca^{2+}} to a POPC membrane 
    %that assumes the stoichiometry of 2~POPC:1~\ce{Ca^{2+}} (details in reference~\citenum{altenbach84}) 
    %provides a good fit to experimental measurements~\cite{altenbach84}
    %and it also provides a good fit to our simulation data. 
    %This supports our statement that the success of the ternary complex model in the experiments
    %can be understood with the atomistic detail of our simulations as an average 
    %stoichiometry of otherwise almost evenly distributed clusters of one cation with 1,2 or 3 lipids (Fig.~\ref{fig:cacl_complexes}). 
    %Note that the units in the reference~\citenum{altenbach84} are different from the units presented here,
    %and, hence, the observed slope of the linear relationship is slightly different.
    }
\end{figure}

>>>>

The results from simulations are shown in Fig.~\ref{fig:cacl-bind}
together with the line fitted to experimental data by Altenbach and Seelig~\cite{altenbach84}.
Both results are in agreement with the prediction of the ternary complex model.
The small discrepancy between the results from experiments and simulations probably
arise from difference in the evaluation of the concentrations and
inaccuracy of Poisson-Boltzmann theory for divalent cations like \ce{Ca^{2+}}~\cite{Andelman1995}. 
In conclusion, the results suggest that the almost equal probabilities for
\ce{Ca^{2+}} to form complexes with one to three lipids detailed in the main text is in line with an averaged interpretation of the experimental observations which supported the ternary complex model.
\newpage
\begin{figure}[!h]
  \centering
  \includegraphics[height=9.0cm,angle=-90]{../Fig/bound-CAs_conc-eccl17.eps}
  \caption{\label{fig:cacl-bind}
    Fits of experimental~\cite{altenbach84} and ECC-POPC simulation data to
    the prediction of the ternary complex model.
    {\color{red} Joe, please change the axes labels to correspond the notation in the text, i.e. $C_b$ and $C_I$,
    and write in the title of simulation fit (red dashed line) that it is the fit to simulation.}
    %Ternary complex binding model of \ce{Ca^{2+}} to a POPC membrane 
    %that assumes the stoichiometry of 2~POPC:1~\ce{Ca^{2+}} (details in reference~\citenum{altenbach84}) 
    %provides a good fit to experimental measurements~\cite{altenbach84}
    %and it also provides a good fit to our simulation data. 
    %This supports our statement that the success of the ternary complex model in the experiments
    %can be understood with the atomistic detail of our simulations as an average 
    %stoichiometry of otherwise almost evenly distributed clusters of one cation with 1,2 or 3 lipids (Fig.~\ref{fig:cacl_complexes}). 
    %Note that the units in the reference~\citenum{altenbach84} are different from the units presented here,
    %and, hence, the observed slope of the linear relationship is slightly different.
    }
\end{figure}
